### 2020-10-21 paper/sections/design.tex
second letter

A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}. Briefly, it is a reinforcement learning-based system to train an agent to choose a proper compression quality level $ c $ for one image to be compressed by JPEG. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections. We provide experimental details of all the hyperparameters in Section.~\ref{Section: evaluation}. %% \\

@@

The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $. For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network as the RL agent. But the naive Deep Q-learning Network can not work well in this task because of the following challenges: %% \\

>>>>

A brief framework of AdaCompress is shown in Figure~\ref{fig: framework}. Briefly, it is a reinforcement learning-based system to train an agent to choose a proper compression quality level $ c $ for one image to be compressed by JPEG. We discuss the formulation, agent design, reinforcement learning-based framework, reward feedback, \emph{inference-estimation-querying-retraining} mechanism, and insight of RL agent's behaviors separately in the following subsections. We provide experimental details of all the hyperparameters in Section~\ref{Section: evaluation}. %% \\

@@

The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $. {\color{revise2} In our design, each compression is treated as a complete RL task that only has one step, and the agent performs the action only once to accomplish the task. The agent is able to learn across consecutive tasks, because the input sequence (i.e., consecutive images likely to be captured by the same camera) shares similar contextual characteristics. The similar design has also been used in previous studies, including RL-based cache strategy \cite{wang2020intelligent_RL,zhong2018deep_RL,sadeghi2019deep_RL}.} For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network as the RL agent. But the naive Deep Q-learning Network can not work well in this task because of the following challenges: %% \\

### 2020-10-21 paper/sections/evaluation.tex
second letter

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Subsection.~\ref{subsec:insight}. The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

@@

In our experiments, we measure the compressed and reference image's file size to obtain the compression rate $ \Delta s $. Since we do not have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric. The formula of $ \mathcal{A} $ is presented in Subsection.~\ref{subsec: formulation}.

>>>>

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}. The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

@@

In our experiments, we measure the compressed and reference image's file size to obtain the compression rate $ \Delta s $. Since we do not have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric. The formula of $ \mathcal{A} $ is presented in Subsection~\ref{subsec: formulation}.

### 2020-10-21 paper/sections/relatedwork.tex
second letter

In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection.~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).

>>>>

In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
